The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-01 paper_draft.Rmd
added other probit regressions

@@

>>>>

```{r generate linear regression table rural sample, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist, model_register), 
               title = "Rural sample linear regression results", 
               label = "fullResults",
               header = F,
               keep = c("floods", "droughts"))
```

```{r probit regression rural sample, echo = F, message = F}

probitMod_assist_r <- glm(assist ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_register_r <- glm(register ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

probitMod_work_r <- glm(work_reason ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = rural, family=binomial(link="probit"))

summary(probitMod_assist_r)  # model summary
summary(probitMod_register_r)
summary(probitMod_work_r)
```

@@

```{r linear regression generate table urban sample, echo = F, results = "asis"}
stargazer::stargazer(list(model_assist, model_register), 
               title = "Urban sample linear regression results", 
               label = "urbanlinearResults",
               header = F,
               keep = c("floods", "droughts"))

```{r probit regression urban sample, echo = F, message = F}

probitMod_assist_u <- glm(assist ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_register_u <- glm(register ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

probitMod_work_u <- glm(work_reason ~ floods + droughts + age + female + lny + child + grandchild + num_children + hhhead_educ + female_hhhead + dept_factor + year_factor, data = urban, family=binomial(link="probit"))

summary(probitMod_assist_r)  # model summary
summary(probitMod_register_r)
summary(probitMod_work_r)
```
